---
title: "Netflix TidyTuesday"
author: "Marieke Jones"
date: "4/20/2021"
output: 
  html_document:
    keep_md: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Load library and dataset

```{r}
library(tidyverse)
library(lubridate)

netflix_titles <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-20/netflix_titles.csv')
netflix_titles
```

Clean up the date
```{r}
head(netflix_titles$date_added)

netflix_titles <- netflix_titles %>%
  mutate(date_added = parse_date(date_added, format = "%B %d, %Y"))
```

Create a basic plot showing the number of TV shows and Movies added over time

```{r}
netflix_titles %>%
  group_by(year = year(date_added)) %>%
  count(type) %>%
  ggplot(aes(year, n)) + geom_line(aes(group = type, color = type))

# see this by month instead
netflix_titles %>%
  mutate(monthyear = floor_date(date_added, "month")) %>% 
  group_by(monthyear) %>%
  count(type) %>%
  ggplot(aes(monthyear, n)) + geom_line(aes(group = type, color = type))
```

Is the number of international titles increasing?

```{r}
netflix_titles %>% count(country) %>% filter(str_detect(country, "United States"))

netflix_titles %>% count(country) %>% filter(country == "United States")

# if it has any other country I'll call it an international film
netflix_titles %>% 
  mutate(international = if_else(country == "United States", "US", "international")) %>% count(international)
         
# make the plot
netflix_titles %>% 
  mutate(international = if_else(country == "United States", "US Only", "International"),
         monthyear = floor_date(date_added, "month")) %>%
  filter(monthyear > "2015-01-01") %>%
  drop_na(international) %>%
  group_by(monthyear) %>%
  count(type, international) %>%
  ggplot(aes(monthyear, n)) + 
  geom_line(aes(group = international, color = international)) + 
  facet_wrap(~type) +
  labs(x = "Date Added to Netflix", y = "Count")
```

Play with the duration

```{r}
netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  count(type)
# all items with duration units of min are all movies
```

See the longest movies (that I never want to watch)

```{r}
netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  arrange(-duration_number) %>%
  select(title, listed_in, duration_number)
```

See the shortest movies - are they all kids movies?

```{r}
netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  arrange(duration_number) %>%
  count(title, listed_in, duration_number)

# count the kids movies
netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  arrange(duration_number) %>%
  head(200) %>%
  count(listed_in) %>%
  arrange(-n)

# make a plot
netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  arrange(duration_number) %>%
  head(200) %>%
  count(listed_in) %>%
  arrange(-n) %>%
  head(20) %>%
  mutate(listed_in = as_factor(listed_in)) %>%
  ggplot(aes(n, listed_in)) + geom_col()

# if the movie is ever listed in Children's turn it red
netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  arrange(duration_number) %>%
  head(200) %>%
  count(listed_in) %>%
  arrange(-n) %>%
  head(20) %>%
  mutate(listed_in = as_factor(listed_in)) %>%
  mutate(red = case_when(str_detect(listed_in, "Children") ~ "red",
                         TRUE ~ "black")) %>%
  ggplot(aes(n, listed_in)) + geom_col(aes(fill = red)) +
  scale_fill_manual(values = c("darkgrey", "salmon")) +
  theme(legend.position = "none") +
  labs(x = "Count", y = "", title = "20 Shortest Movies on Netflix")
```

Are children's movies decreasing in duration over time?

Clean up the listed_in to create some cleaner genres

```{r}
netflix_titles %>% 
  filter(type == "Movie") %>%
  count(listed_in) %>% 
  arrange(-n)

top6genre <- netflix_titles %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  mutate(genre = case_when(
    str_detect(listed_in, "Children") ~ "Children & Family",
    str_detect(listed_in, "Comed") ~ "Comedy",
    str_detect(listed_in, "Drama") ~ "Drama",
    str_detect(listed_in, "Roman") ~ "Romance",
    str_detect(listed_in, "Action") ~ "Action & Adventure",
    str_detect(listed_in, "Documentar") ~ "Documentary",
    str_detect(listed_in, "Horror") | 
      str_detect(listed_in, "Thrill") ~ "Horror & Thriller",
                         TRUE ~ listed_in)) %>%
  count(genre) %>%
  arrange(-n) %>%
  head(6)
```

Make the plot
```{r}
theme_set(theme_minimal() + theme(legend.position = 'blank'))

netflix_titles %>%
  filter(release_year >= 1980) %>%
  separate(duration, into = c("duration_number", "duration_units"), sep = " ") %>%
  mutate(duration_number = as.numeric(duration_number)) %>%
  filter(duration_units == "min") %>%
  mutate(genre = case_when(
    str_detect(listed_in, "Children") ~ "Children & Family",
    str_detect(listed_in, "Comed") ~ "Comedy",
    str_detect(listed_in, "Drama") ~ "Drama",
    str_detect(listed_in, "Roman") ~ "Romance",
    str_detect(listed_in, "Action") ~ "Action & Adventure",
    str_detect(listed_in, "Documentar") ~ "Documentary",
    str_detect(listed_in, "Horror") | str_detect(listed_in, "Thrill") ~ "Horror & Thriller",
                         TRUE ~ listed_in)) %>%
  filter(genre %in% top6genre$genre) %>%
  group_by(genre, release_year) %>%
  summarize(Duration = mean(duration_number)) %>%
  ggplot(aes(release_year, Duration)) + 
  geom_line(aes(group = genre, color = genre)) +
  facet_wrap(~genre) +
  labs(x = "", y = "Average Movie Duration (min)", title = "Children's movies and Dramas decrease in duration over time")
```

